\newcommand \maxsubs {10 }
\section*{Instructions}
\begin{itemize}

\item \textbf{Collaboration Policy}: Please read the collaboration policy in the syllabus.
\item\textbf{Late Submission Policy:} See the late submission policy in the syllabus.
\item\textbf{Submitting your work:} You will use Gradescope to submit
  answers to all questions\ifthenelse{\equal{\homeworktype}{\string written}}{}{ and code}. 

\begin{itemize}
    
    % IF NOT USING TEMPLATE: 
    % \item \textbf{Written:} You will submit your completed homework as a PDF to Gradescope. For each problem, please clearly indicate the question number (e.g. 3.2). Submissions can be handwritten, but must be clearly legible; otherwise, you will not be awarded marks.   Alternatively, submissions can be written in \LaTeX{}. You may use the \LaTeX{} source of this assignment (included in the handout .zip) as your starting point. For multiple choice / select all questions, simply write the letter(s) (e.g. A, B, C) corresponding to your chosen answer.
    % IF USING TEMPLATE: 
    \item \textbf{Written:} You will submit your completed homework as a PDF to Gradescope. Please use the provided template. Submissions can be handwritten, but must be clearly legible; otherwise, you will not be awarded marks. Alternatively, submissions can be written in \LaTeX{}. Each answer should be within the box provided. 
    %If you do not follow the template or your submission is misaligned, your assignment may not be graded correctly by our AI assisted grader. 
    If you do not follow the template, your assignment may not be graded correctly by our AI assisted grader and there will be a \textbf{\textcolor{red}{2\% penalty}} (e.g., if the homework is out of 100 points, 2 points will be deducted from your final score).
    
    \ifdefempty{\overleafUrl}{}{
    \item \textbf{\LaTeX{} Source:} \overleafUrl
    }

    \ifthenelse{\equal{\homeworktype}{\string written}}{}{
    \item \textbf{Programming:} You will submit your code for programming questions to Gradescope. \ifthenelse{\equal{\autograder}{\string yes}}{}{ There is no autograder. }
    We will examine your code by hand and may award marks for its submission.
    }{}
   
  \end{itemize}
  
\ifthenelse{\equal{\homeworktype}{\string written}}{}{\item\textbf{Materials:} The data that you will need in order to complete this assignment is posted along with the writeup and template on the course website.}

\end{itemize}

\begin{center}
    \pointtable[v][questions]
\end{center}